Supplementary Material

### 2023-11-08 output/paper/figures.qmd
Checked compliance to guidenlines for figures and tables.

- Number figures according to the order in which they are first mentioned in the main text.
- Clearly label all axes, giving both the measure and the unit of measurement.
- Smallest type size: 8pt.
- Maximum width: 7 inches in portrait, 9 inches in landscape mode.
- Multi-panel figures: capital letters followed by closing parenthesis, completely above and to the left of the panel.
- Use log-scale when plotting relative measures of effects.
- Figure titles and legends should be submitted as single paragraph.
- The text of figure legends typed after the reference list.
- Save and submit each main text figure as an individual file (PDF with fonts embedded).

# Participants

- Flow diagram: number of individuals at each stage of study. Report numbers potentially eligible, examined for eligibility, confirmed eligible, included in the study, completing follow-up, and analysed.

@@

- Forest plot for RQ2 (group by chemical class, and for each chemical group bars for metabolites) and RQ3.

@@

```{r marginal-2}
#| label: fig-marginal-2
#| fig-cap: Average comparisons
#| fig-width: 10
#| fig-height: 10

>>>>

- Use log-scale when plotting relative measures of effects.
- Figure titles and legends should be submitted as single paragraph.

@@

@@

```{r marginal-2}
#| label: fig-marginal-2
#| fig-cap: Average comparisons
#| fig-width: 9
#| fig-height: 10

### 2023-11-08 output/paper/manuscript.qmd
Modified pipeline so that targets for processing results do not actually produce eg plots but only ready to use tibbles for plots and tables. Tested pipeline to create paper but I think I still have to manually reference tables and figures in manuscript.
Checked compliance to guidenlines for figures and tables.

- The title should be less or equal than 300 characters. It should indicate the study design, the subject of the paper, information regarding exposures and outcomes assessed, and whether the study was observational or experimental.
- The suggested length of the abstract is less or equal than 300 words.
- The suggested length is <7,000 words, excluding abstract, references, tables, figure captions, acknowledgments, and Supplementary Material.
  - Concise sub-headings should be less or equal than 8 words, and they should be used to organize information rather than summarize the results.
  - In-text citations with superscript numbers: outside periods and commas, but inside colons and semicolons.

@@

@@

- Give the source of funding and the role of the funders for the present study and, if applicable, for the original study on which the present article is based.

@@

{{< embed tables.qmd >}}

>>>>

- Authorship must follow the ICMJE's criteria. Author names should be listed in ScholarOne and author contributions should be detailed in the cover letter ("Author A..."). Neither names nor contributions should appear in the blinded manuscript. Do not include conflicts of interest.
- The use of the word "effect(s)" as a proxy for "association(s)" is discouraged.
- The length of the abstract must be less or equal than 200 words, and should be unstructured, stating the research questions, the methods used, and the results and conclusions of the research.
- The length must be <4,000 words, excluding abstract, references, tables, figure captions, acknowledgments, and Supplementary Material.
  - Use the AMA format.
  - In-text citations: full-sized Arabic numerals in parentheses within the sentence.
- Submission: SER members receive a 10% discount on the fees per page. This should be requested in the cover letter. Also 20% discount for Open Access charges. If uploading a single file (document, tables, figures, SM), designate the file as "Main document - anonymous".

@@

**Do not use "Introduction" as a heading**.

@@

@@

### 2023-11-08 output/paper/sections/methods.qmd
Tested pipeline w/ vector of id_val.
Checked compliance to guidenlines for figures and tables.

@@

- Methods for selecting potential confounders (provide DAGs).
- Describe all statistical methods with assumptions, including those used to control for confounding.
  - Description of outcome model, weighting method, estimand, and balance assessment.
  - Description of method used to estimate effects (e.g., g-computation).
  - Description of method used for SE and CI.
- Describe any methods used to examine subgroups and interactions (sub-group analysis or moderation analysis or analysis of effect-modification).
- Explain how missing data were addressed.
- Cohort study: explain how loss to follow-up was addressed.
- Cross-sectional study: describe analytical methods taking account of sampling strategy.
- Describe any sensitivity analyses.
- When referring to previous publications for methods' details, include a brief description of the approach, key assumptions and limitations, and any deviation.
- Names and version numbers for the used software packages, including non-data arguments if deviating from the default ones.

>>>>

- For RQ1 I used creatinine values from HELIX. For RQ3 the ones from the steroids dataset. For RQ2, I included in the model both variables.

@@

- In RQ2, I included the logarithm of the denominator in the RHS. In RQ3, I used the logarithm of the ratio in the RHS.

- Methods for selecting potential confounders (provide DAGs).
- Whenever possible, mathematical equations should be written on a single line. For multiplication, use a times sign.
- Describe all statistical methods with assumptions, including those used to control for confounding.
  - Description of outcome model, weighting method, estimand, and balance assessment.
  - Description of method used to estimate effects (e.g., g-computation).
  - Description of method used for SE and CI.
- Describe any methods used to examine subgroups and interactions (sub-group analysis or moderation analysis or analysis of effect-modification).
- Explain how missing data were addressed.
- Cohort study: explain how loss to follow-up was addressed.
- Cross-sectional study: describe analytical methods taking account of sampling strategy.
- Describe any sensitivity analyses.
- When referring to previous publications for methods' details, include a brief description of the approach, key assumptions and limitations, and any deviation.
- Names and version numbers for the used software packages, including non-data arguments if deviating from the default ones.

### 2023-11-08 output/paper/si.qmd
Checked compliance to guidenlines for figures and tables.

```{r}
source("code/proc_res.R")
```

@@

num_digits_est = 3
num_digits_sig = 2
```

- Should be limited to results of secondary analyses and background details needed to ensure transparency:
  - Questionnaires.
  - Tables and figures with results of sensitivity analyses.
  - Tables with numeric data corresponding to results shown in the main text figures.
  - DAGs used to select model covariates.
- Text description of study methods should NOT go in the SM.
- Number supplemental tables and figures separately according to the order in which they are first mentioned in the main text, using an "S" prefix.

@@

- Provide the title for each table above the table and the notes below the table.

@@

- Detailed characteristics of study participants (demographic, clinical, social), by cohort and overall.

@@

@@

- Provide the title for each figure below the figure on the same manuscript page as the figure itself.

@@

- ADRF and AMEF for RQ2 and RQ3.
- Whole distribution (i.e., density) of e.g., risk differences (instead of marginalized estimates), with lines for mean and median.

@@

```{r marginal-2sa}
#| label: fig-marginal-2sa
#| fig-cap: Average comparisons for effect modification
#| fig-width: 10
#| fig-height: 10

>>>>

```{r}
source("code/dictionary.R")
source("code/data.R")
source("code/proc_res.R")
```

@@

id_var <- "HelixID"
num_digits_est = 3
num_digits_sig = 2
```

- Files for supplementary data must be accompanied by a summary of the file names and types.

@@

@@

@@

### Description of chemicals

```{r info-chems}
#| label: tbl-info-chems
#| tbl-cap: Information about non-persistent EDCs

edcs_info <- myphd::edcs_information() |>
  tidylog::select(-c(chem_id, smiles, ctd_id, exposome_explorer_id)) |>
  tidylog::mutate(
    var = janitor::make_clean_names(
      edcs_info$short_name,
      replace = c(`-` = ""),
      case = "none"
    ) |>
      tolower()
  ) |>
  tidylog::relocate(var, .after = short_name)
gt::gt(edcs_info,
       groupname_col = "class") |>
  gt::sub_values(
    values = c("NA"),
    replacement = ""
  ) |>
  gt::cols_label(
    full_name = "Compound",
    short_name = "Symbol",
    var = "Variable name",
    pubchem_cid = "PubChem CID",
    parental_compound = "Parental compound"
  ) |>
  gt::tab_style(
    locations = gt::cells_row_groups(group = dplyr::everything()),
    style = list(gt::cell_text(weight = "bold"))
  )
```

### Description of metabolites

```{r info-mets}
#| label: tbl-info-mets
#| tbl-cap: Information about metabolites

mets_info <- readODS::read_ods(
  path = "docs/steroids.ods"
) |>
  tidylog::select(analyte, acronym, type, hmdb_id, cas_number)
gt::gt(mets_info,
       groupname_col = "type") |>
  gt::sub_values(
    values = c("NA"),
    replacement = ""
  ) |>
  gt::cols_label(
    analyte = "Metabolite",
    acronym = "Symbol",
    hmdb_id = "HMDB ID",
    cas_number = "CAS number"
  ) |>
  gt::tab_style(
    locations = gt::cells_row_groups(group = dplyr::everything()),
    style = list(gt::cell_text(weight = "bold"))
  ) |>
  gt::tab_footnote(
    footnote = "Human Metabolome Database",
    locations = gt::cells_column_labels(
      columns = hmdb_id
    )
  ) |>
  gt::tab_footnote(
    footnote = "Chemical Abstracts Service",
    locations = gt::cells_column_labels(
      columns = cas_number
    )
  )
```

@@

### Description of chemicals

```{r desc-chems-lod}
#| label: fig-desc-chems
#| fig-cap: Description of chemicals
#| fig-width: 6
#| fig-height: 7

viz_desc_vars(
  dat = load_dat_request()$dat,
  vars = vars_of_interest(append_to_chem = "cdesc")$chemicals,
  fct_levels = c(1, 2, 3, 4),
  is_chem = TRUE
)
```

### Description of metabolites

```{r desc-mets-lod}
#| label: fig-desc-mets
#| fig-cap: Description of metabolites
#| fig-width: 6
#| fig-height: 7

viz_desc_vars(
  dat = myphd::extract_cohort(load_steroids()$desc,
                              id_var = id_var) |>
    tidylog::mutate(
      cohort = dplyr::case_when(
        cohort == "EDE" ~ "EDEN",
        cohort == "KAN" ~ "KANC",
        cohort == "MOB" ~ "MOBA",
        cohort == "RHE" ~ "RHEA",
        .default = cohort
      )
    ),
  vars = vars_of_interest()$metabolites |>
    paste0("_cdesc"),
  fct_levels = c(1, 2, 3, 4),
  is_chem = FALSE
)
```

@@

@@

```{r marginal-2sa}
#| label: fig-marginal-2sa
#| fig-cap: Average comparisons for effect modification
#| fig-width: 9
#| fig-height: 10
